Finite Property Convex Elicitation Paper

### 2019-01-25 cvx-fin.tex
minor fix
meeting notes / todos

\begin{definition}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is:
  \begin{itemize}
  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$, 
  \begin{align*}
  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]
  \end{align*}
  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
  \end{itemize}
\end{definition}

It is also interesting to contrast the definitions above with the following.
\begin{definition}
  A \emph{strong link} is a function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
\end{definition}

@@

% \begin{definition}\label{def:strip-and-trim}
% 	\jessie{strip, trim}
% 	For $\Gamma:\simplex \toto \R'$, define $\strip(\Gamma) = \{\Gamma_r : r \in \R' \}$.
% 	If $\Gamma$ has a finite set of full-dimensional level sets that union to $\simplex$, there is a finite property $\gamma:\simplex \toto \R$ such that $\strip(\gamma) := \trim(\Gamma)$.
% 	\jessie{Fix without over-explaining.}
% \end{definition}

@@

	The following are equivalent:
	\begin{enumerate}
		\item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
		\item The set $\{\Gamma_r : r \in \R \}$ is finite.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}
For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
Thus, the set $\Theta$ generated by indexing a finite set is finite.
For $2 \implies 3$, if any level set is not full-dimensional, it is the subset of a full-dimensional level set, so we can remove it while keeping the property nondegenerate.
Thus, this set $\Theta$ is still finite, consists of full-dimensional level sets, and unions to $\simplex$

@@

For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.

\end{proof}

\begin{theorem}
  Every polyhedral loss embeds a finite elicitable property.
\end{theorem}

\begin{theorem}
  Every finite elicitable property is $(n-1)$-embeddable.
\end{theorem}
\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}

@@

\begin{theorem}
  A polyhedral loss indirectly elicits a finite elicitable property $\gamma$ if and only if it embeds a property which refines $\gamma$.
\end{theorem}

@@

@@

We can summarize the above in the following theorem.
\begin{theorem}
  Let $\gamma$ be a finite elicitable property.
  Then $\gamma$ is 1-embeddable if and only if it is orderable.
  In particular, if $\eliccvx(\gamma)=1$, then $\elicpoly(\gamma) = \elicembed(\gamma)=1$.
\end{theorem}

@@

>>>>

\begin{definition}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is:
  \begin{itemize}
  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$, 
  \begin{align*}
  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]~.
  \end{align*}
  \item \emph{Exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
  \end{itemize}
\end{definition}

It is also interesting to contrast the definitions above with the following.
\begin{definition}
  A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
\end{definition}

@@

\begin{definition}\label{def:trim}
  \jessie{trim}
\end{definition}
\raf{Explain why this is a useful concept in general, and for convex elic}

@@

  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
  \item $\trim(\Gamma)$ is a finite set.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
\end{proposition}
\begin{proof}
For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
Thus, the set $\Theta$ generated by indexing a finite set is finite.
For $2 \implies 3$, if any level set is not full-dimensional, it is the subset of a full-dimensional level set, so we can remove it while keeping the property nondegenerate.
Thus, this set $\Theta$ is still finite, consists of full-dimensional level sets, and unions to $\simplex$

@@

For the second part, in order for $\psi$ to be separated, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
If the loss $L$ is polyhedral, then we can construct a $\psi$ so that the above holds.
If no such $\psi$ existed, then for some $p$ such that $u \in \arginf_{z \in \R} \E_p L(z,Y)$, we know there is a $\delta > 0$ such that $\E_p L(v,Y) - \E_p L(u,Y) < \delta$ by continuity of $L$.
Additionally, if $\psi$ was not selective, then we know $\psi(v) = \psi(w)$ for some embedded point $w \neq u$.
Since the losses of $u$ and $v$ are not bounded about away from each other and $\psi(v) = \psi(w)$, then the loss $L$ must be constant on $\conv(\{u,v,w\})$, otherwise we would either contradict elicitability of $\Gamma$ or the construction of the calibrated link $\psi$.
Therefore, we can reassign $\psi(v) = \psi(u)$ for any $v\in B(\epsilon, u)$, and such a link additionally separated.
\end{proof}

\begin{theorem}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
\end{theorem}
\raf{Also mention here that \emph{every} non-redundant elicitable property is $(n-1)$-embeddable.}

@@

\begin{theorem}
  Every polyhedral loss embeds a finite elicitable property.

  $+$

  A polyhedral loss indirectly elicits a finite elicitable property $\gamma$ if and only if it embeds a property which refines $\gamma$.
\end{theorem}

\raf{But wait, what about dimension?}

@@

\raf{Note: move monotone and lemmas to appendix}

@@

We can summarize the above in the following theorem.
\raf{TFAE}
\begin{theorem}
  Let $\gamma$ be a finite elicitable property.
  Then $\gamma$ is 1-embeddable if and only if it is orderable.
  In particular, if $\eliccvx(\gamma)=1$, then $\elicpoly(\gamma) = \elicembed(\gamma)=1$.
  \raf{add $elic$ for continuous non-loc-const properties}
\end{theorem}

@@

\raf{Use orderable to motivate}
